Future Cosmic Microwave Background delensing with galaxy surveys.

### 2017-07-09 Notes/galaxy_delensing.tex
typos

\title{Future Cosmic Microwave Background delensing with galaxy surveys.}         % Enter your title between curly braces
\author{A. Manzotti}        % Enter your name between curly braces
\email{manzotti.alessandro@gmail.com}
\affiliation{Kavli Institute for Cosmological Physics, University of Chicago}
\affiliation{Department of Astronomy and Astrophysics, University of Chicago, 5640 South Ellis Avenue, Chicago, IL 60637, USA}
\date{\today}

        % Enter your date or \today between curly braces
\begin{abstract}

@@

Furthermore, we are not considering the uncertainties on galaxy survey internal parameters such as biases, source distributions and photometric redshift uncertainties. These uncertaintes can significantly degrade inflationary constraints \cite{sherwin:2015,namikawa:2016a}.
However, as shown in \cite{sherwin:2015,namikawa:2016a}, these can be auto-calibrated i.e. they can be tightly constrained using galaxy survey auto- and cross-correlation spectra. We checked this for a few of the tracer combinations used here and find it particularly true once several tracers are jointly taken into account.
Finally, although we have assumed a Gaussian covariance $\sigma( C_{\ell}^{BB} )$ it actually has small non-Gaussian contributions \cite{motloch:2017,benoit-levy:2012}. This approximation is good enough to show the improvement due to delensing.

@@

Even for CMB S4, galaxy surveys will still play an important role.
For example, a tomographically binned LSST-survey will remove 56\% of the lensing power. While this performance is comparable to a Stage-3 CMB it will allow to probe the robustness against systematics of an eventual detection.
Indeed delensing with just CMB data will require a careful study of possible biases and systematics effects due to the use of the same source (the CMB) we are delensing to reconstruct the lensing effect itself \cite{carron:2017,sehgal:2016,namikawa:2017}.
For this reason, efficient galaxies tracers are not only useful in the short term but will also play a role in cross-checking these internal biases.

@@

% ===================
%\onecolumngrid
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1.]{../images/errors_summary.pdf}
\caption{\relook{to be filled with final results}}
\label{fig}
\end{center}
\end{figure}
\twocolumngrid

>>>>

\title{Future Cosmic Microwave Background delensing with galaxy surveys.}       
\author{A. Manzotti} 
\email{manzotti.alessandro@gmail.com}
\affiliation{Kavli Institute for Cosmological Physics, University of Chicago}
\affiliation{Department of Astronomy and Astrophysics, University of Chicago, 5640 South Ellis Avenue, Chicago, IL 60637, USA}
\date{\today}
\begin{abstract}

@@

Furthermore, we are not considering the uncertainties on galaxy survey internal parameters such as biases, source distributions and photometric redshift uncertainties. These uncertaintes can significantly degrade inflationary constraints \cite{sherwin:2015,namikawa:2016a}.
However, as shown in \cite{sherwin:2015,namikawa:2016a}, these can be auto-calibrated i.e. they can be tightly constrained using galaxy survey auto- and cross-correlation spectra. We checked this for a few of the tracer combinations used here and find it particularly true once several tracers are jointly taken into account.
Finally, although we have assumed a Gaussian covariance $\sigma( C_{\ell}^{BB} )$ it actually has small non-Gaussian contributions \cite{motloch:2017,benoit-levy:2012}. This approximation is good enough to show the improvement due to delensing.
The approximations made here go in the direction of a slightly optimistic \textit{absolute} value for the parameters statistical uncertainties both for the standard and the delensed case. The delensing improvement is defined as the \textit{relative} value of these uncertainties $\alpha_{i} = \sigma^{\rm{del}}(i)/\sigma(i)$ and, at first order, it is not affected by this assumptions.

@@

Even for CMB S4, galaxy surveys will still play an important role.
For example, a tomographically binned LSST-survey will remove 56\% of the lensing power. While this performance is comparable to a Stage-3 CMB it will allow to probe the robustness against systematics of an eventual detection.
Indeed delensing with just CMB data will require a careful study of possible biases and systematics effects due to the use of the same source (the CMB) we are delensing to reconstruct the lensing effect itself \cite{carron:2017,sehgal:2016,namikawa:2017}.
For this reason, efficient galaxies tracers are not only useful in the short term but will also play a role in cross-checking these internal biases. 
% ===================
\onecolumngrid
\begin{figure}[htbp]
\begin{center}
\includegraphics[scale=1]{../images/errors_summary.pdf}
\caption{\relook{to be filled with final results}}
\label{fig}
\end{center}
\end{figure}
\twocolumngrid

@@
